\documentclass[margin-section]{resume}

\begin{document}

% Heading information
\name{Holly A. French}
\address{48 Douglass\\San Francisco, CA 94114}
\address{(949) 338-6971\\hollyafrench90@gmail.com\\github.com/phrenchphry11}

\begin{resume}

    % Professional Experience -------------------------------------------------
    \section{Professional\\Experience}

    % Pandora
    \employer{Pandora Radio (via Rdio acquisition)}
    \location{Oakland, California}

    \title{Software Developer}
    \dates{January 2016 -- Present}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        % Dev
        \item Member of Pandora's Ad Targeting and Delivery team:
        \begin{list2}
            \item Responsible for managing ad tracking stats.
            \item Implemented logging for number of serves, impressions, and clicks per ad, which gets stored in Redis, Hadoop, and StatsD.
            \item Created periodic Hadoop and Redis reports on ad stats to monitor overall trends and individual stats per ad.
            \item Refactored acceptance tests in Python, and ported them over to use the PyTest library.
        \end{list2}
    \end{list2}
    \end{position}

    % Rdio
    \employer{Rdio}
    \location{San Francisco, California}

    \title{Software Developer}
    \dates{July 2014 -- December 2015}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        % Dev
        \item Member of Rdio's Backend Features team until acquisition by Pandora:
        \begin{list2}
            \item Responsible for developing and maintaining internal Django APIs, admin pages, email daemons, and MySQL database migrations.
            \item Built the APIs and subscription logic of Rdio Select, Rdio’s mid-level, lower cost monthly subscription tier.
            \item Developed features for Rdio Live, a partnership with radio stations around the world to stream live radio through the Rdio web app and fully integrate live music streams into the product.
        \end{list2}
    \end{list2}

    % Rdio
    \employer{Piazza Technologies, Inc.}
    \location{Palo Alto, California}

    \title{Software Developer}
    \dates{June 2013 -- June 2014}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        % Dev
        \item Designed and developed Piazza's real-time in-class polls feature launched on iOS, Android, and our web client.
        \begin{list2}
            \item Implemented the frontend and backend for polls on the web.
            \item Did hands-on customer development to drive the initial spec and iterate on feedback by meeting with professors and students.
        \end{list2}
        \item Implemented the backend to support push notifications for Piazza’s Android app.
    \end{list2}

    % Education ---------------------------------------------------------------
    \section{Education}

    \title{Bachelor of Arts in Computer Science}
    \employer{Carleton College}
    \dates{September 2009 -- June 2013}
    \location{Northfield, Minnesota}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Graduated \emph{Cum Laude}.
    \end{list2}
    \end{position}

    % Technical Skills --------------------------------------------------------
    \section{Skills}
        \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Experienced in Python, Django, Java, SQL, Redis, Git, Perforce.
        \item Proficient in Hive, HTML/CSS, iOS, JavaScript, JQuery, Mercurial, MongoDB, Ruby, Swift.
    \end{list2}
    \end{position}

    % Technical Training --------------------------------------------------------
    \section{Training}

    \title{Introduction to iOS Programming in Swift}
    \employer{Codepath}
    \dates{May 2015}
    \location{San Francisco, California}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Completed a 10-week course in iOS Programming through Codepath.
        \item The course culminated in a final project, where I created a public transit scheduling app.
    \end{list2}
    \end{position}

    % Technical Awards --------------------------------------------------------
    % \section{Awards}

    % Volunteer --------------------------------------------------------
    \section{Volunteer Experience}

    \title{Mentor}
    \employer{Hackbright Academy}
    \dates{July 2015 -- Present}
    \location{San Francisco, California}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Hackbright Academy is a software engineering school for women. We provide guidance for women on technical engineering questions, career advice, and job interview preparation.
    \end{list2}
    \end{position}

    \title{Organizer}
    \employer{Django Girls}
    \dates{November 2014 \& December 2015}
    \location{San Francisco, California}

    \begin{position}
    \vspace{-\baselineskip}
    \begin{list2}
        \item Django Girls is a crash course in Django for beginning women coders. We provide curriculum and resources for a group of 30 students to complete a two-day introduction to Python and Django.
    \end{list2}
    \end{position}

    %\textbf{}

\end{resume}
\end{document}
